---
title: ""
author: ""
output:
  rmarkdown::html_document:
    theme: lumen
---


```{r setup, echo = FALSE, include=FALSE, warning = FALSE}

library(knitr)
library(writexl)
library(rgdal)
library(sf) ## Read shapefiles
library(dplyr)
library(leaflet)
library(cowplot)
library(ggplot2)
library(plotly)
library(readxl)
library(htmlwidgets)

```

```{r image, fig.show = "asis", out.width = c("25%", "50%"), fig.align = "default", echo = FALSE, warning = FALSE}

ggdraw() + draw_image("/Users/wemigliari/Documents/R/R_Scripts/Rmarkdown/para/images/logo_ufopa.png")
ggdraw() + draw_image("/Users/wemigliari/Documents/R/R_Scripts/Rmarkdown/para/images/logo_programa_pos.png")


```


```{r, echo=FALSE, warning=FALSE, comment = FALSE, message = FALSE, include = FALSE}

library(readxl)
library(plotly)

data <- read_excel("/Users/wemigliari/Documents/R/data/para/para_propriedades.xlsx")
data <- data.frame(data)
data[data=="X"]<-0
data[data=="-"]<-0
data[is.na(data)] <- 0

#class(data)

data[, c(5:43)] <- sapply(data[, c(5:43)], as.factor)

data[, c(5:43)] <- sapply(data[, c(5:43)], as.numeric)

```

## Supply Chains & Land Use
#### Property size is one of the determinants linked to the exportation of commodities in the Amazônia Legal. The following graphs represent the extension of each property in the State of Pará considering the municipalities and the representation of each ownership (ha) on total area (ha).

\
\
Pesquisador\
Dr. Wellington Migliari\
Institut de Recerca TransJus\
Universitat de Barcelona\

\
Supervisor\
Dr. Itamar Paulino\
Programa de Pós-graduação 
Sociedade, Ambiente e Qualidade de Vida\
Universidade Federal do Oeste do Pará\

\
\

## {.tabset}

### Land Use & Large Properties
```{r, echo = FALSE, warning=FALSE, comment=FALSE, message=FALSE, fig.width=10}

## Area 100-200 ha
plot_ly(data, marker = list(symbol = 'circle', size = data$area_100_200/3000, color = I(data$color),
                            line = list(width = 1, color = 'black'), opacity=0.5)) %>%
  add_markers(x = data$area_hec, y = data$area_100_200, z = data$num_unid_100_200, color = ~factor(data$State), showlegend = T)%>%
  layout(
    title = "Area (ha) and Size of the Properties, Pará",
    scene = list(
      xaxis = list(title = "x = Total Area (ha)"),
      yaxis = list(title = "y = Size, 100-200 ha"),
      zaxis = list(title = "z = Units"),
      camera = list(eye = list(x = 2, y = 2, z = 2))
    ))

```
Fonte: [IBGE](https://www.ibge.gov.br/estatisticas/economicas/agricultura-e-pecuaria/21814-2017-censo-agropecuario.html?edicao=21858&t=resultados).
\
\
```{r, echo = FALSE, warning=FALSE, comment=FALSE, message=FALSE, fig.width=10}

## Area 200-500 ha
plot_ly(data, marker = list(symbol = 'circle', size = data$area_200_500/4000, color = I(data$color),
                            line = list(width = 1, color = 'black'), opacity=0.5)) %>%
  add_markers(x = data$area_hec, y = data$area_100_200, z = data$num_unid_200_500, color = ~factor(data$State), showlegend = T)%>%
  layout(
    title = "Area (ha) and Size of the Properties, Pará",
    scene = list(
      xaxis = list(title = "x = Total Area (ha)"),
      yaxis = list(title = "y = Size, 200-500 ha"),
      zaxis = list(title = "z = Units"),
      camera = list(eye = list(x = 2, y = 2, z = 2))
    ))

```
Fonte: [IBGE](https://www.ibge.gov.br/estatisticas/economicas/agricultura-e-pecuaria/21814-2017-censo-agropecuario.html?edicao=21858&t=resultados).
\
\
```{r, echo = FALSE, warning=FALSE, comment=FALSE, message=FALSE, fig.width=10}

## Area 500-1000 ha
plot_ly(data, marker = list(symbol = 'circle', size = data$area_500_mil/4000, color = I(data$color),
                            line = list(width = 1, color = 'black'), opacity=0.5)) %>%
  add_markers(x = data$area_hec, y = data$area_500_mil, z = data$num_unid_500_mil, color = ~factor(data$State), showlegend = T)%>%
  layout(
    title = "Area (ha) and Size of the Properties, Pará",
    scene = list(
      xaxis = list(title = "x = Total Area (ha)"),
      yaxis = list(title = "y = Size, 500-1000 ha"),
      zaxis = list(title = "z = Units"),
      camera = list(eye = list(x = 2, y = 2, z = 2))
    ))

```
Fonte: [IBGE](https://www.ibge.gov.br/estatisticas/economicas/agricultura-e-pecuaria/21814-2017-censo-agropecuario.html?edicao=21858&t=resultados).
\
\
```{r, echo = FALSE, warning=FALSE, comment=FALSE, message=FALSE, fig.width=10}

## Area 1000 a 2000 ha
plot_ly(data, marker = list(symbol = 'circle', size = data$area_mil_dois/6000, color = I(data$color),
                            line = list(width = 1, color = 'black'), opacity=0.5)) %>%
  add_markers(x = data$area_hec, y = data$area_mil_dois, z = data$num_unid_mil_dois, color = ~factor(data$State), showlegend = T)%>%
  layout(
    title = "Area (ha) and Size of the Properties, Pará",
    scene = list(
      xaxis = list(title = "x = Total Area (ha)"),
      yaxis = list(title = "y = Size, 1000-2000 ha"),
      zaxis = list(title = "z = Units"),
      camera = list(eye = list(x = 2, y = 2, z = 2))
    ))

```
Fonte: [IBGE](https://www.ibge.gov.br/estatisticas/economicas/agricultura-e-pecuaria/21814-2017-censo-agropecuario.html?edicao=21858&t=resultados).
\
\
```{r, echo = FALSE, warning=FALSE, comment=FALSE, message=FALSE, fig.width=10}

## Area 2,500 up to 10,000 ha
plot_ly(data, marker = list(symbol = 'circle', size = data$area_dois_mil_meio_10/10000, color = I(data$color),
                            line = list(width = 1, color = 'black'), opacity=0.5)) %>%
  add_markers(x = data$area_hec, y = data$area_dois_mil_meio_10, z = data$num_unid_dois_mil_meio_10, color = ~factor(data$State), showlegend = T)%>%
  layout(
    title = "Area (ha) and Size of the Properties, Pará",
    scene = list(
      xaxis = list(title = "x = Total Area (ha)"),
      yaxis = list(title = "y = Size, 2,500-10,000 ha"),
      zaxis = list(title = "z = Units"),
      camera = list(eye = list(x = 2, y = 2, z = 2))
    ))

```
Fonte: [IBGE](https://www.ibge.gov.br/estatisticas/economicas/agricultura-e-pecuaria/21814-2017-censo-agropecuario.html?edicao=21858&t=resultados).
\
\
```{r, echo = FALSE, warning=FALSE, comment=FALSE, message=FALSE, fig.width=10}

## Area + 10,000 ha
plot_ly(data, marker = list(symbol = 'circle', size = data$area_10_mil_mais/10000, color = I(data$color),
                            line = list(width = 1, color = 'black'), opacity=0.5)) %>%
  add_markers(x = data$area_hec, y = data$area_10_mil_mais, z = data$num_unid_10_mil_mais, color = ~factor(data$State), showlegend = T)%>%
  layout(
    title = "Area (ha) and Size of the Properties, Pará",
    scene = list(
      xaxis = list(title = "x = Total Area (ha)"),
      yaxis = list(title = "y = Size, + 10,000 ha"),
      zaxis = list(title = "z = Units"),
      camera = list(eye = list(x = 2, y = 2, z = 2))
    ))

```
Fonte: [IBGE](https://www.ibge.gov.br/estatisticas/economicas/agricultura-e-pecuaria/21814-2017-censo-agropecuario.html?edicao=21858&t=resultados).
\
\